Regression Analysis—Simple

### 2019-07-15 figures/gatekeeper_author_outcomes/gatekeeper_author_outcomes.Rmd
updated figure files for new submission

@@

countries_separate <- elife %>%
  filter(full_decision_made & has_full_submission & ca_country %in% countries) %>%
  group_by(ca_country, la_country_homophily) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE, na.rm = T),
    encourage_accept_rate = accept_count / paper_count,
    se = 1.96 * sqrt( (encourage_accept_rate * (1 - encourage_accept_rate)) / paper_count),
    encourage_accept_rate = encourage_accept_rate * 100,
    se = se * 100,
    lower = encourage_accept_rate - se,
    upper = encourage_accept_rate + se,
    upper = ifelse(upper > 100, 100, upper)
  ) %>%
  group_by(ca_country) %>%
  mutate(totals = sum(paper_count)) %>%
  ungroup() %>%
  left_join(sig_df) %>%
  #top_n(16, totals) %>% # 8 countries, 3 authorship types per country, therefore first 24 rows
  mutate(ca_country = factor(sapply(as.character(ca_country), simpleCap))) %>%
  # Start ggplot
  ggplot(aes(x = la_country_homophily, y = encourage_accept_rate, fill = la_country_homophily)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
  geom_text(aes(label = paper_count, y = 7.5), size = 4) +
  geom_text(aes(label = sig, x = 1.5, y = 86), size = 4) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 80, 101), yend = ifelse(sig != "N/A", 80, 101)), color = "black") +
  facet_wrap(~ca_country, nrow = 2, ncol = 4, labeller = label_wrap_gen()) +
  theme_dakota() +
  guides(fill = FALSE) +
  scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
  scale_y_continuous(limits = c(0, 100), position = "right") +
  scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
  labs(
    x = "",
    y = "% of full submissions accepted",
    title = "D"
  ) +
  theme(
    axis.text.x = element_text(size = 11, angle = 330, vjust = 1, hjust = 0, face = "bold"),
    axis.title.y = element_text(size = 12)
  )

@@

countries_pooled <- d1.summ %>%
  union(d2.summ) %>%
  union(d25.summ) %>%
  #union(d3.summ) %>%
  left_join(sig_df, by = "type") %>%
  mutate(type = factor(type, 
                       levels = c("all", "no us", "no usuk"),
                       labels = c("All Countries", "No U.S.", "No U.S., U.K.")
                       )
         ) %>%
  ggplot(aes(x = la_country_homophily, y = encourage_accept_rate, fill = la_country_homophily)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
  geom_text(aes(label = paper_count, y = 10), size = 4) +
  geom_text(aes(label = sig, x = 1.5, y = 85), size = 4) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 80, 101), yend = ifelse(sig != "N/A", 80, 101)), color = "black") +
  facet_wrap(~type, ncol = 4, labeller = label_wrap_gen(20)) +
  coord_cartesian(ylim = c(0.0, 100)) +
  theme_dakota() +
  guides(fill = FALSE) +
  ylim(0, 1) +
  scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
  scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
  scale_y_continuous(position = "right") +
  labs(
    x = "",
    y = "% of full submissions accepted",
    title = "C"
  ) +
  theme(axis.text.x = element_text(size = 11, angle = 330, vjust = 1, hjust = 0, face = "bold"),
        axis.title.y = element_text(size = 12))

>>>>

```{r}
library(ggrepel)
head(data_homophily)
gender_homophily <- data_homophily %>%
  mutate(composition = factor(composition, levels = c("All-female", "Mixed-gender", "All-male"))) %>%
  ggplot(aes(x = composition, y = acceptance_rate, color = gender, shape = gender, group = gender)) +
  geom_line() +
  geom_point(size = 3.5) +
  facet_wrap(~author_key, ncol = 1) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.1) + 
  coord_cartesian(ylim = c(30, 80)) +
  geom_text_repel(aes(hjust = -0.5, vjust = -1, label = paste0(round(acceptance_rate, 1), "%"))) +
  theme_dakota() +
  scale_color_discrete(name = "Author Gender") +
  scale_shape_discrete(name = "Author Gender") +
  labs(y = "% of full submissions accepted",
       x = "Reviewer Team Composition",
       title = "A") +
  theme(axis.title.x = element_text(face = "bold", size = 11),
        axis.text.x = element_text(face = "bold"),
        legend.title = element_text(size = 11),
        legend.text = element_text(size = 10),
        legend.position = "bottom",
        strip.text.x = element_text(size = 12),
        strip.text.y = element_text(size = 14, face = "bold"))

gender_homophily
ggsave("~/Desktop/elife_lineplot.png", gender_homophily, height = 7, width = 7)
```

@@

countries_separate <- elife %>%
  filter(full_decision_made & has_full_submission & ca_country %in% countries) %>%
  group_by(ca_country, la_country_homophily) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE, na.rm = T),
    encourage_accept_rate = accept_count / paper_count,
    se = 1.96 * sqrt( (encourage_accept_rate * (1 - encourage_accept_rate)) / paper_count),
    encourage_accept_rate = encourage_accept_rate * 100,
    se = se * 100,
    lower = encourage_accept_rate - se,
    upper = encourage_accept_rate + se,
    upper = ifelse(upper > 100, 100, upper)
  ) %>%
  group_by(ca_country) %>%
  mutate(totals = sum(paper_count)) %>%
  ungroup() %>%
  left_join(sig_df) %>%
  #top_n(16, totals) %>% # 8 countries, 3 authorship types per country, therefore first 24 rows
  mutate(ca_country = factor(sapply(as.character(ca_country), simpleCap))) %>%
  # Start ggplot
  ggplot(aes(x = la_country_homophily, y = encourage_accept_rate, fill = la_country_homophily)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
  geom_text(aes(label = paper_count, y = 7.5), size = 4) +
  geom_text(aes(label = sig, x = 1.5, y = 86), size = 4) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 80, 101), yend = ifelse(sig != "N/A", 80, 101)), color = "black") +
  facet_wrap(~ca_country, nrow = 2, ncol = 4, labeller = label_wrap_gen()) +
  theme_dakota() +
  guides(fill = FALSE) +
  scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
  scale_y_continuous(limits = c(0, 100), position = "right") +
  scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
  labs(
    x = "",
    y = "% of full submissions accepted",
    title = "C"
  ) +
  theme(
    axis.text.x = element_text(size = 11, angle = 330, vjust = 1, hjust = 0, face = "bold"),
    axis.title.y = element_text(size = 12)
  )

@@

countries_pooled <- d1.summ %>%
  union(d2.summ) %>%
  union(d25.summ) %>%
  #union(d3.summ) %>%
  left_join(sig_df, by = "type") %>%
  mutate(type = factor(type, 
                       levels = c("all", "no us", "no usuk"),
                       labels = c("All Countries", "No U.S.", "No U.S., U.K.")
                       )
         ) %>%
  ggplot(aes(x = la_country_homophily, y = encourage_accept_rate, fill = la_country_homophily)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
  geom_text(aes(label = paper_count, y = 10), size = 4) +
  geom_text(aes(label = sig, x = 1.5, y = 85), size = 4) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 80, 101), yend = ifelse(sig != "N/A", 80, 101)), color = "black") +
  facet_wrap(~type, ncol = 4, labeller = label_wrap_gen(20)) +
  coord_cartesian(ylim = c(0.0, 100)) +
  theme_dakota() +
  guides(fill = FALSE) +
  ylim(0, 1) +
  scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
  scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
  scale_y_continuous(position = "right") +
  labs(
    x = "",
    y = "% of full submissions accepted",
    title = "B"
  ) +
  theme(axis.text.x = element_text(size = 11, angle = 330, vjust = 1, hjust = 0, face = "bold"),
        axis.title.y = element_text(size = 12))

### 2019-07-15 figures/regression_analysis/regression_analysis_interaction.rmd
updated figure files for new submission

### Define initial and full submissions
```{r}
# First, filter the data by removing the observations from Antarctica 
# add a variable for "included"
initial_submissions <- elife %>% filter(initial_decision_made)
initial_submissions$included <- with(initial_submissions, initial_decision_made & ca_continent != "Antarctica" & !is.na(ca_institution_rank) & !is.na(ca_gender) & !is.na(ca_se_dist) & !is.na(se_gender))

@@

@@

```{r}
main_effects_tidy <- tidy(main_effects, conf.int = T, exponentiate = T) %>%
  mutate(type = "Main Effects")
standard_interaction_tidy <- tidy(standard_interaction, conf.int = T, exponentiate = T) %>%
  mutate(type = "With Interaction")
mixed_only_tidy <- tidy(mixed, conf.int = T, exponentiate = T) %>%
  mutate(type = "Mixed Reviewers Only")
all_male_only_tidy <- tidy(all_male, conf.int = T, exponentiate = T) %>%
  mutate(type = "All-Male Reviewers Only")
global_tidy <- tidy(full_model, conf.int = T, exponentiate = T) %>%
  mutate(type = "Global Interactions")

@@

both.full.plots <- all_models %>%
  filter(type == "Global Interactions" | type == "Main Effects") %>%
  filter(term != "(Intercept)") %>%
  mutate(
    type = factor(type, 
                  levels = c("Main Effects", "Global Interactions"),
                  labels = c("A. Main Effects", "B. Global Interactions")),
    ast = sig2ast(p.value),
    ast.factor = factor(ast, 
                 levels = c("ns", ".", "*", "**", "***"), 
                 labels = c("p > 0.1", "p < 0.1", "p < 0.05", "p < 0.01", "p < 0.001")),
    color.sig = ifelse(p.value < 0.1, ifelse(estimate > 1, "Positive", "Negative"), "Not Signigicant"),
    term = as.factor(term),
    term = plyr::revalue(term, full.cov.labels),
    term = reorder(term, estimate)
  ) %>%
  ggplot(aes(x = term, y = estimate, color = color.sig, shape = ast.factor)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  coord_flip() +
  facet_grid(~type) +
  geom_text(aes(label = paste0(round(estimate, 3), 
                               ifelse(ast %in% c("ns", "."), "", ast))),
            vjust = -0.6, hjust = -0.1, show.legend = F) +
  scale_color_manual(name = "Direction of Effect", values = c("firebrick", "grey", "blue")) +
  scale_shape_manual(name = "Significance Level", values = c(1, 10, 16, 17, 18)) +
  geom_hline(yintercept = 1, color = "black") +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        strip.text = element_text(size = 12, face = "bold"),
        axis.text.y = element_text(size = 11)) +
  labs(y = "Odds Ratio")

@@

stargazer(main_effects, standard_interaction, all_male, mixed, full_model,
          type = "latex",
          style = "ajs",
          ci = T, 
          align = T, 
          apply.coef = exp,
          t.auto = F,
          p.auto = F,
          column.labels = c("Main Effects", "With interaction", "Only All-Male", "Only Mixed", "Global Interaction"),
          covariate.labels = all.cov.labels)

@@

### Save the plot
```{r}
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/main/", figure_name, figure_extension)
ggsave(name, plot = both.full.plots, height = 8, width = 10)
```

>>>>

### Define initial and full submissions
```{r}
# First, filter the data by removing the observations from Antarctica 
# add a variable for "included"
initial_submissions <- elife %>% filter(initial_decision_made)
initial_submissions$included <- with(initial_submissions, initial_decision_made & ca_continent != "Antarctica" & !is.na(ca_institution_rank) & !is.na(ca_gender) & !is.na(ca_se_dist))

@@

```{r}
exp <- glm(accepted ~ submission_year + submission_type + fa_gender + la_institution_rank + la_gender + la_continent + I(la_reviewer_dist/ 1000000) + la_reviewer_dist_zero + composition + la_gender:composition, data = subset(full_with_inter, included & composition != "All Women"), family = "binomial")
anova(exp, test = "Chisq")
summary(exp)
```

@@

```{r}
main_effects_tidy <- tidy(main_effects, conf.int = T, exponentiate = T) %>%
  mutate(type = "Main Effects")
standard_interaction_tidy <- tidy(standard_interaction, conf.int = T, exponentiate = T) %>%
  mutate(type = "With Interaction")
mixed_only_tidy <- tidy(mixed, conf.int = T, exponentiate = T) %>%
  mutate(type = "Mixed Reviewers Only")
all_male_only_tidy <- tidy(all_male, conf.int = T, exponentiate = T) %>%
  mutate(type = "All-Male Reviewers Only")
global_tidy <- tidy(full_model, conf.int = T, exponentiate = T) %>%
  mutate(type = "With Interactions")

@@

both.full.plots <- all_models %>%
  filter(type == "With Interactions" | type == "Main Effects") %>%
  filter(term != "(Intercept)") %>%
  mutate(
    type = factor(type, 
                  levels = c("Main Effects", "With Interactions"),
                  labels = c("A. Main Effects", "B. With Interactions")),
    ast = sig2ast(p.value),
    ast.factor = factor(ast, 
                 levels = c("ns", ".", "*", "**", "***"), 
                 labels = c("p > 0.1", "p < 0.1", "p < 0.05", "p < 0.01", "p < 0.001")),
    color.sig = ifelse(p.value < 0.1, ifelse(estimate > 1, "Positive", "Negative"), "Not Signigicant"),
    term = as.factor(term),
    term = plyr::revalue(term, full.cov.labels),
    term = reorder(term, estimate)
  ) %>%
  ggplot(aes(x = term, y = estimate, color = color.sig, shape = ast.factor)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  coord_flip(ylim = c(0.1, 3)) +
  facet_grid(~type) +
  geom_text(aes(label = paste0(round(estimate, 3), 
                               ifelse(ast %in% c("ns", "."), "", ast))),
            vjust = -0.6, hjust = -0.1, show.legend = F) +
  scale_color_manual(name = "Direction of Effect", values = c("firebrick", "grey", "blue")) +
  scale_shape_manual(name = "Significance Level", values = c(1, 10, 16, 17, 18)) +
  geom_hline(yintercept = 1, color = "black") +
  theme_minimal() +
  guides(color = guide_legend(title.position = "top"),
         shape = guide_legend(title.position = "top")) +
  theme(axis.title.y = element_blank(),
        strip.text = element_text(size = 12, face = "bold"),
        legend.position = "bottom",
        axis.text.y = element_text(size = 11)) +
  labs(y = "Odds Ratio")

@@

stargazer(main_effects, standard_interaction, all_male, mixed, full_model,
          type = "latex",
          style = "ajs",
          ci = T, 
          align = T, 
          apply.coef = exp,
          t.auto = F,
          p.auto = F,
          column.labels = c("Main Effects", "With interaction", "Only All-Male", "Only Mixed", "With Interaction"),
          covariate.labels = all.cov.labels)

@@

### Save the plot
```{r}
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/main/", figure_name, figure_extension)
ggsave(name, plot = both.full.plots, height = 8, width = 11)
```

### 2019-07-15 figures/regression_analysis/regression_analysis_simple.rmd
updated figure files for new submission

```{r}
initial.plot <- initial_tidy %>%
  filter(term != "(Intercept)") %>%
  mutate(
    #type = factor(type, levels = c("Main Effects", "Global Interactions")),
    ast = sig2ast(p.value),
    ast.factor = factor(ast, 
                 levels = c("ns", ".", "*", "**", "***"), 
                 labels = c("p > 0.1", "p < 0.1", "p < 0.05", "p < 0.01", "p < 0.001")),
    color.sig = ifelse(p.value < 0.1, ifelse(estimate > 1, "Positive", "Negative"), "Not Signigicant"),
    term = as.factor(term),
    term = plyr::revalue(term, initial.cov.labels),
    term = reorder(term, estimate)
  ) %>%
  ggplot(aes(x = term, y = estimate, color = color.sig, shape = ast.factor)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  coord_flip() +
  #facet_grid(~type, scales = "free") +
  geom_text(aes(label = paste0(round(estimate, 3), 
                               ifelse(ast %in% c("ns", "."), "", ast)), 
                x = term, y = estimate), vjust = -0.6, hjust = -0.1, show.legend = F) +
  scale_color_manual(name = "Direction of Effect", values = c("firebrick", "grey", "blue")) +
  scale_shape_manual(name = "Significance Level", values = c(1, 10, 16, 17, 18), drop = F) +
  geom_hline(yintercept = 1, color = "black") +
  ylim(0.1, 6) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_text(size = 9),
        plot.title = element_text(size = 12, face = "bold")) +
  labs(y = "Odds Ratio",
       title = "A. Initial Submissions")

@@

```{r}
full.plot <- full_tidy %>%
  filter(term != "(Intercept)") %>%
  mutate(
    ast = sig2ast(p.value),
    ast.factor = factor(ast, 
                 levels = c("ns", ".", "*", "**", "***"), 
                 labels = c("p > 0.1", "p < 0.1", "p < 0.05", "p < 0.01", "p < 0.001")),
    color.sig = ifelse(p.value < 0.1, ifelse(estimate > 1, "Positive", "Negative"), "Not Signigicant"),
    term = as.factor(term),
    term = plyr::revalue(term, full.cov.labels),
    term = reorder(term, estimate)
  ) %>%
  ggplot(aes(x = term, y = estimate, color = color.sig, shape = ast.factor)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  coord_flip() +
  #facet_grid(~type, scales = "free") +
  geom_text(aes(label = paste0(round(estimate, 3), 
                               ifelse(ast %in% c("ns", "."), "", ast)), 
                x = term, y = estimate), vjust = -0.6, hjust = -0.1, show.legend = F) +
  scale_color_manual(name = "Direction of Effect", values = c("firebrick", "grey", "blue")) +
  scale_shape_manual(name = "Significance Level", values = c(1, 10, 16, 15, 18), drop = F) +
  geom_hline(yintercept = 1, color = "black") +
  ylim(0.1, 6) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_text(size = 9),
        plot.title = element_text(size = 12, face = "bold")) +
  labs(y = "Odds Ratio",
       title = "B. Full Submissions")

@@

both.plots <- grid.arrange(arrangeGrob(initial.plot + theme(legend.position="none"),
                         full.plot + theme(legend.position="none"),
                         nrow=1),
             mylegend, ncol=2,widths=c(10, 2))

@@

### Save the output
```{r}
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/main/", figure_name, figure_extension)
ggsave(name, plot = both.plots, height = 6, width = 10)
```

>>>>

```{r}
initial.plot <- initial_tidy %>%
  filter(term != "(Intercept)") %>%
  mutate(
    #type = factor(type, levels = c("Main Effects", "Global Interactions")),
    ast = sig2ast(p.value),
    ast.factor = factor(ast, 
                 levels = c("ns", ".", "*", "**", "***"), 
                 labels = c("p > 0.1", "p < 0.1", "p < 0.05", "p < 0.01", "p < 0.001")),
    color.sig = ifelse(p.value < 0.1, ifelse(estimate > 1, "Positive", "Negative"), "Not Signigicant"),
    term = as.factor(term),
    term = plyr::revalue(term, initial.cov.labels),
    term = reorder(term, estimate)
  ) %>%
  ggplot(aes(x = term, y = estimate, color = color.sig, shape = ast.factor)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  coord_flip() +
  #facet_grid(~type, scales = "free") +
  geom_text(aes(label = paste0(round(estimate, 3), 
                               ifelse(ast %in% c("ns", "."), "", ast)), 
                x = term, y = estimate), vjust = -0.6, hjust = -0.1, show.legend = F) +
  scale_color_manual(name = "Direction of Effect", values = c("firebrick", "grey", "blue")) +
  scale_shape_manual(name = "Significance Level", values = c(1, 10, 16, 17, 18), drop = F) +
  geom_hline(yintercept = 1, color = "black") +
  coord_flip(ylim = c(0.1, 3)) +
  theme_minimal() +
  guides(color = guide_legend(title.position = "top"),
         shape = guide_legend(title.position = "top")) +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_text(size = 9),
        legend.position = "bottom",
        plot.title = element_text(size = 12, face = "bold")) +
  labs(y = "Odds Ratio",
       title = "A. Initial Submissions")

@@

```{r}
full.plot <- full_tidy %>%
  filter(term != "(Intercept)") %>%
  mutate(
    ast = sig2ast(p.value),
    ast.factor = factor(ast, 
                 levels = c("ns", ".", "*", "**", "***"), 
                 labels = c("p > 0.1", "p < 0.1", "p < 0.05", "p < 0.01", "p < 0.001")),
    color.sig = ifelse(p.value < 0.1, ifelse(estimate > 1, "Positive", "Negative"), "Not Signigicant"),
    term = as.factor(term),
    term = plyr::revalue(term, full.cov.labels),
    term = reorder(term, estimate)
  ) %>%
  ggplot(aes(x = term, y = estimate, color = color.sig, shape = ast.factor)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  #coord_flip() +
  #facet_grid(~type, scales = "free") +
  geom_text(aes(label = paste0(round(estimate, 3), 
                               ifelse(ast %in% c("ns", "."), "", ast)), 
                x = term, y = estimate), vjust = -0.6, hjust = -0.1, show.legend = F) +
  scale_color_manual(name = "Direction of Effect", values = c("firebrick", "grey", "blue")) +
  scale_shape_manual(name = "Significance Level", values = c(1, 10, 16, 15, 18), drop = F) +
  geom_hline(yintercept = 1, color = "black") +
  coord_flip(ylim = c(0.1, 3)) +
  theme_minimal() +
  guides(color = guide_legend(title.position = "top"),
         shape = guide_legend(title.position = "top")) +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_text(size = 9),
        legend.position = "bottom",
        plot.title = element_text(size = 12, face = "bold")) +
  labs(y = "Odds Ratio",
       title = "B. Full Submissions")

@@

both.plots <- grid.arrange(arrangeGrob(initial.plot + theme(legend.position="none"),
                         full.plot + theme(legend.position="none"),
                         nrow=1),
             mylegend, nrow=2,heights=c(10, 2))

@@

### Save the output
```{r}
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/main/", figure_name, figure_extension)
ggsave(name, plot = both.plots, height = 8, width = 8)
```
